%
%  progress-presentation.tex
%  src
%
%  Created by Illya Starikov on 09/16/17.
%  Copyright 2017. Illya Starikov. All rights reserved.
%

% \documentclass[notes,xcolor=dvipsnames]{beamer}       % print frame + notes
% \documentclass[notes=only,xcolor=dvipsnames]{beamer}  % only notes
% \documentclass[xclolor=dvipsnames]{beamer}            % only frames
\documentclass[handout,xclolor=dvipsnames]{beamer}    % only frames, no pauses
\usepackage{soul,graphics}

\input{template-presentation/macros.tex}
\title{A Special Presentation (Presentation \#1)}
\subtitle{Special Topics (CS3001)}
\author{Illya Starikov}
\date{Sometimes In The Future}
\institute{Missouri University of Science and Technology}

\begin{document}
\begin{darkframes}
    \maketitle

    \begin{frame}
        \frametitle{A Brief Introduction}

        \begin{itemize}
            \item Generally, excelled at presenting. \pause{}
            \item These were not without a lot of effort. \pause{}
            \item I would generally spend several hours practicing presentation.\pause{} I hope to change that for this class.\pause{}
            \item From here on out, every presentation will generally improved.\pause{} (I don't know if this is allowed but better to ask for forgiveness than permission).
            \item Why?
        \end{itemize}
    \end{frame}

    \begin{frame}
        \frametitle{A Brief Introduction}

        Because of the massive workload this semester, I did not get to work on this skill after the first day. I had to skip class regularly to make hours at work. However, I was able to learn some things from it.
    \end{frame}

    \begin{frame}
        \frametitle{Prior Knowledge}

        \begin{itemize}
                \item I attended some improv sessions last semester.
                \item Besides that, I had no prior knowledge.
        \end{itemize}
    \end{frame}

    \begin{frame}
        \frametitle{Goals}

        \begin{itemize}
            \item To be able to give a good, improv-ed presentation.
        \end{itemize}
    \end{frame}


    \begin{frame}
        \frametitle{Goal Accomplishment}

        \begin{itemize}
            \item I successfully gave a winged presentation during the first lecture. Although it made me really nervous, after I got used to it, I felt a bit better about myself.
        \end{itemize}
    \end{frame}

    \begin{frame}
        \frametitle{In Closing}

        Thank you for having me! All question, comments, and insults can be directed towards me:

        \begin{center}
            \begin{description}
                \item[\faComment] \href{mailto:starikov@mst.edu}{starikov@mst.com}
                \item[\faLinkedin] \href{https://www.linkedin.com/in/illyastarikov/}{Illya Starikov}
                \item[\faGithub] \href{https://github.com/IllyaStarikov/}{Illya Starikov}
                \item[\faRss] \href{https://freneticarray.com/}{FreneticArray.com}
            \end{description}
        \end{center}
    \end{frame}
\end{darkframes}
\end{document}
