%
%  progress-presentation.tex
%  src
%
%  Created by Illya Starikov on 09/16/17.
%  Copyright 2017. Illya Starikov. All rights reserved.
%

% \documentclass[notes,xcolor=dvipsnames]{beamer}       % print frame + notes
% \documentclass[notes=only,xcolor=dvipsnames]{beamer}  % only notes
\documentclass[xclolor=dvipsnames]{beamer}            % only frames
%\documentclass[handout,xclolor=dvipsnames]{beamer}    % only frames, no pauses
\usepackage{soul,graphics}

\input{template-presentation/macros.tex}
\title{Unit Tests (Presentation \#2)}
\subtitle{Special Topics (CS3001)}
\author{Illya Starikov}
\date{Sometimes In The Future}
\institute{Missouri University of Science and Technology}

\begin{document}
\begin{darkframes}
    \maketitle

    \begin{frame}
        \frametitle{A Brief Introduction}

        \begin{itemize}
            \item Good code is broken into many functions.
            \item In a perfect world, these functions would always produce the right results.
            \item Unfortunately, this isn't a perfect world.
            \item Unit tests allow to test all these blocks to guarantee correctness.
        \end{itemize}
    \end{frame}

    \begin{frame}
        \frametitle{Prior Knowledge}

        \begin{itemize}
            \item I started writing unit tests last semester for my internship (in C\#).
            \item However, they were small and minimal.
        \end{itemize}
    \end{frame}

    \begin{frame}
        \frametitle{Goals}

        \begin{itemize}
            \item To become fluent in several unit testing frameworks.
            \item To become better at penetration testing of functions.
        \end{itemize}
    \end{frame}

    \begin{frame}[fragile]
        \frametitle{Tangible Evidence}
        \framesubtitle{Python Unit Tests (AI)}

        \footnotesize
        \begin{lstlisting}[language=Python]
def test_grid_size(self):
    not_long_enough = [list(range(2)), list(range(2)), list(range(2))]

    rows, columns = 5, 7
    just_right = [list(range(columns)) for i in range(rows)]

    self.assertRaises(AssertionError, MechanicalMatch.grid_size, not_tall_enough)

    grid_rows, grid_columns = MechanicalMatch.grid_size(just_right)
    self.assertEqual(grid_rows, rows)
    self.assertEqual(grid_columns, columns)
        \end{lstlisting}
    \end{frame}

    \begin{frame}[fragile]
        \frametitle{Tangible Evidence}
        \framesubtitle{C++ Unit Tests (Numerical Modeling)}

        \footnotesize
        \begin{lstlisting}[language=C++]
SECTION("Stream Operator") {
    auto polarPair = PolarPair<R, Theta>(defaultModulus, defaultArgument);
    std::stringstream expected, actual;

    polarPair.setPrecision(6);

    expected << std::setprecision(6) << std::fixed << "(" << defaultModulus << ", " << defaultArgument << ")";
    actual << polarPair;

    REQUIRE(expected.str() == actual.str());
}
        \end{lstlisting}
    \end{frame}

    \begin{frame}[fragile]
        \frametitle{Tangible Evidence}
        \framesubtitle{C\# Unit Tests (Work)}

        I can't shared source code from my work because of security reasons/non disclosure agreements.
    \end{frame}

    \begin{frame}
        \frametitle{Resources}

        \begin{itemize}
            \item Online resources.
                \begin{itemize}
                    \item \href{https://github.com/catchorg/Catch2}{C++ Unit Tests.}
                    \item \href{https://msdn.microsoft.com/en-us/library/hh694602.aspx}{C\# Unit Tests.}
                    \item \href{https://docs.python.org/2/library/unittest.html}{Python Unit Tests.}
                \end{itemize}

            \item Looking at other people's source code.
            \item Discussing ideas with boss and coworkers.
        \end{itemize}
    \end{frame}

    \begin{frame}
        \frametitle{Goal Accomplishment}

        \begin{itemize}
            \item Since the beginning of the semester, I have drastically become better at writing unit tests.
            \item I am fluent in writing unit tests in C++, C\#, and Python.
            \item Although I have gotten better at writing unit tests, I could progress a lot more.
        \end{itemize}
    \end{frame}

    \begin{frame}
        \frametitle{In Closing}

        Thank you for having me! All question, comments, and insults can be directed towards me:

        \begin{center}
            \begin{description}
                \item[\faComment] \href{mailto:starikov@mst.edu}{starikov@mst.com}
                \item[\faLinkedin] \href{https://www.linkedin.com/in/illyastarikov/}{Illya Starikov}
                \item[\faGithub] \href{https://github.com/IllyaStarikov/}{Illya Starikov}
                \item[\faRss] \href{https://freneticarray.com/}{FreneticArray.com}
            \end{description}
        \end{center}
    \end{frame}
\end{darkframes}
\end{document}
