%
%  1.1-functions.tex
%  chapter-1
%
%  Created by Illya Starikov on 05/17/17.
%  Copyright 2017. Illya Starikov. All rights reserved.
%

\subsection{Review of Functions}
A \textbf{function} is a rule that assigns to each value $x$ in a set $D$ a unique value denoted $f(x)$. The set $D$ is the \textbf{domain} of the function. The \textbf{range} is the set of all values of $f(x)$ produced as $x$ varies over the domain.

\subsubsection{Vertical Line Test}
A graph represents a function if and only  if it passes the \textbf{vertical line test}. Every vertical line intersects the graph at most once. A graph that fails this test does not represent a function.

\subsubsection{Composite Functions}
Given two functions $f$ and $g$, the composite functions $f \circ g$ is defined by $(f \circ g)(x) = f(g(x))$. It is evaluated in two steps: $y = f(u)$, where $u = g(x)$. The domain of $f \circ g$ consists of all $x$ in the domain of $g$ such that $u = g(x)$ is in the domain of $f$.

\subsubsection{Symmetry in Functions}
An \textbf{even function} has the property that $f(-x) = f(x)$, for all $x$ in the domain. The graph of an even function symmetric about the y-axis. Polynomials consisting of only even powers of the variable (of the form $x^{2n}$, where $n$ is a nonnegative integer) are even functions.

An \textbf{odd function} $f$ has the property that $f(-x) = -f(x)$, for all $x$ in the domain. The graph of an odd function is symmetric about the origin. Polynomials consisting of only odd powers of the variable (of the form $x^{2n + 1}$, where $n$ is a nonnegative integer) are odd functions.