\documentclass[oneside,12pt]{scrbook}

\input{template/macros}

\newcommand{\titlepagename}{Communication Protocol}
\newcommand{\titledescript}{A RESTful guide to the communication of Splatoonio}
\newcommand{\versionNumber}{1.0}
\newcommand{\lastEditAuthor}{Illya Starikov}
\newcommand{\documentStatus}{Draft} % Draft, Proposed, Validated, Approved

\begin{document}
\input{template/titlepage}

\begin{itemize}
    \item The server sends time in every response.
    \item What are users for leaderboard $x$ for page $y$ of size $z$.
    \item What are the achievements for user?
        \begin{itemize}
            \item Send the \texttt{userID}.
            \item Send back all the achievement information.
        \end{itemize}

    \item Query for full board (send checksum, if not equal to server's version, get back full board).

    \item User $x$ requests to join a private game (specific \texttt{gameID}).
    \item User $x$ requests to join ``the'' public game (special \texttt{gameID}).
        \begin{itemize}
            \item Send back new \texttt{playerID} for the game (privacy).
            \item Send back \texttt{gameID}.
            \item Send back full board data.
        \end{itemize}

    \item Player queries if the game is ready.

    \item Player $x$ moved to location lat/lon (player updates server and gets back board update).
        \begin{itemize}
            \item Send pixels painted and timestamp when each pixel was painted.
            \item Send player speed --- anti-spoofing handling.
            \item Send back board diff (list of pixels that changed since last update to this player).
            \item Send back new items and which items were acquired.
        \end{itemize}

    \item Player $x$ acquired/moved over \texttt{itemID}.
        \begin{itemize}
            \item Send back true if the requesting player.
            \item Successfully acquired the item.
        \end{itemize}
\end{itemize}
\end{document}
