%
%  progress-presentation.tex
%  src
%
%  Created by Illya Starikov on 09/16/17.
%  Copyright 2017. Illya Starikov. All rights reserved.
%

% \documentclass[notes,xcolor=dvipsnames]{beamer}       % print frame + notes
% \documentclass[notes=only,xcolor=dvipsnames]{beamer}  % only notes
% \documentclass[xclolor=dvipsnames]{beamer}            % only frames
\documentclass[handout,xclolor=dvipsnames]{beamer}    % only frames, no pauses
\usepackage{soul,graphics}

\input{template-presentation/macros}
\title{Presentation \#2}
\subtitle{Senior Design (Comp Sci 4096)}
\author{Illya Starikov, Ian Howell, Deacon Seals, Michael Harrington, Luke Parton, Eric Michalak, Adam Evans}
\date{Sometimes In The Future}
\institute{Missouri University of Science and Technology}

\begin{document}
\begin{darkframes}
    \maketitle

    \hugeslide{Announcements}
    \begin{frame}
        \frametitle{The Name}

        After a lot of consideration, bureaucracy, and arguing about voting systems, we have settled on the following: \pause{}

        \vspace{3mm}
        \begin{quote}
            \centering {\fontsize{30}{40}\selectfont War Paint}
        \end{quote}
    \end{frame}


    \hugeslide{Product}


    \begin{frame}
        \frametitle{The Product Today}
        \framesubtitle{Besides, You Know, \textbf{Awesome}}

        \begin{itemize}
            \item Still a real-time collaborative game focused on users trying to paint as much of a map as possible.
            \item However, now it has a name.
            \item Picked our hosting provider (Digital Ocean) and found optimal plan.
                \begin{itemize}
                    \item ``we have hosted it; it's just not yet hosted''--Eric Michalak.
                \end{itemize}
        \end{itemize}
    \end{frame}


    \begin{frame}
        \frametitle{What We Still Want To Do}
        \framesubtitle{Before End of Semester, Before We Launch, Before We Die}

        Before the end of the semester$\ldots$
        \begin{itemize}
            \item Finish the iOS application, Android application, and server.
            \item Switch software stacks a couple of times again.
        \end{itemize}\pause{}

        Before we launch a minimal viable product$\ldots$
        \begin{itemize}
            \item Create unit test and do more user testing for the product.
            \item Polish UI elements, create fake scenarios to demonstrate.
        \end{itemize}\pause{}

        Before we die$\ldots$
        \begin{itemize}
            \item Set foot on each of the seven continents.
            \item Make love on a tropical beach.
            \item Run a marathon.
        \end{itemize}
    \end{frame}


    \hugeslide{Costumer}


    \begin{frame}
        \frametitle{Costumers}
        \framesubtitle{Our Real-World Test \st{Monkeys} Subjects}

        Currently, we are bouncing ideas off of:
        \begin{itemize}
            \item Fellow teammates.
            \item Fellow computer students.
            \item ACM members.
        \end{itemize}

        Also, a possibility of ACM sponsored mini-launch.
    \end{frame}


    \begin{frame}
        \frametitle{Costumers}
        \frametitle{What They're Saying}

        \begin{quote}
            ``It sounds cool'' --- Mom\pause{}
        \end{quote}

        \begin{quote}
            ``Dope'' --- Kevin Schoonover, ACM\pause{}
        \end{quote}

        \begin{quote}
            ``$\frac{\star\star\star\star}{\star\star\star\star\star}$, would recommend'' --- Wall Street Journal\pause{}
        \end{quote}

        \begin{quote}
            ``Stop asking us for a review'' --- Nilay Patel, The Verge\pause{}
        \end{quote}

        \begin{quote}
            ``Well it doesn't suck'' --- Illya
        \end{quote}
    \end{frame}


    \hugeslide{Lessons Learned}


    \begin{frame}
        \begin{itemize}
            \item \st{Being a hipster is hard} picking software stacks is hard\pause{}
                \begin{itemize}
                    \item Objective C\textrightarrow Swift 3\textrightarrow Swift 4\pause{}
                    \item Falcon\textrightarrow Flask\pause{}
                    \item Python\textrightarrow Go\pause{}
                    \item Java\textrightarrow\pause{} Dumpster. We've always used Kotlin\pause{}
                \end{itemize}

            \item Naming things (and Cache Invalidations) is hard.\pause{}
            \begin{itemize}
                \item Before picking a name, had to pick a voting system.
                \item After picking voting system, had to determine set of popular names.
                \item Vote for said names.
            \end{itemize}

            \item Determining what to wear to the presentations is hard.

            \item However, all of our go-to tools have worked well --- Git, \LaTeX{}, etc.
        \end{itemize}
    \end{frame}


    \hugeslide{Questions?}


    \begin{frame}
        \frametitle{In Closing}

        Spam Adam Evans (Team Lead) or Illya Starikov (PR/Angel Investing) with all questions, comments, and insults.

        \begin{center}
            \begin{description}
                \item[\faComment] Adam Evans --- \href{mailto:ane3md@mst.edu}{\nolinkurl{ane3md@mst.edu}}
                \item[\faComment] Illya Starikov --- \href{mailto:starikov@mst.edu}{\nolinkurl{starikov@mst.com}}
            \end{description}
        \end{center}

        Special thanks to the awesome team.

        \begin{center}
            \begin{description}
                \item[\faUser] Ian Howell
                \item[\faUser] Deacon Seals
                \item[\faUser] Michael Harrington
                \item[\faUser] Luke Parton
                \item[\faUser] Eric Michalak
            \end{description}
        \end{center}

        \presentby{Illya Starikov}{0}
    \end{frame}
\end{darkframes}
\end{document}
